NFC and burnout in teachers - A replication and extension study

### 2022-07-25 Manuscript/Revision_Letter.Rmd
wrote some answer to the last comment

>>>>

Thank you for this suggestion.
The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
Each part is relevant but not "long enough" to warrant its own paper.

\Assignment{JZ \& AS \& AS}
\WorkInProgress
